Parallel Hierarchical Clustering using \\ Rank-Two Nonnegative Matrix Factorization \thanks{Identify applicable funding agency here. If none, delete this.}

### 2020-07-11 latex/paper.tex
hyperspectral and document descriptions

\GB{Lawton, can you add these descriptions?}
\begin{itemize}

>>>>

\begin{itemize}
	\item \textit{Document Clustering}:
	These datasets are represented by sparse matrices in term frequency-inverdse document frequency (TFIDF) format.
	The rows of these matrices represent words and the columns represent individual documents. Each value in the matrix is a TFIDF statistic for
	a specific word in a document.

	For H2NMF, we used two popular document clustering datasets: Reuters Newswire Topic Classification (Reuters-21578) and \dots
	\LM{I can't find the official name for PubMed or a link to it}

	The Reuters matrix is $12411\times 7984$ and is a preprocessed version of Reuters-21578 used in the SmallK implementation of H2NMF.
	The preprocessed version is the 20 largest prelabeled classes of documents with only single class labels. 
	\LM{Prof Park, is this explanation of Reuters correct?}
	As Reuters is small, it is mainly used as a comparison tool between the ours and the SmallK implmentation.

	The PubMed matrix is $141043\times 8200000$. It is not preprocessed and represents the full size dataset in TFIDF format. This version is
	better suited for scaling as is it is much larger than Reuters and is a good representation of large text classification datasets.

	\item \textit{Hyperspectral Imaging}:
	The images chosen for this dataset follow a similar pattern to Document Clustering. We chose two datasets: the Hyperspectral digital imagery
	collection experiment (HYDICE) image of the Washington DC Mall and the Airborne Visible/Infrared Image Spectrometer (AVIRIS) image 
	of the DC area.

	The images are formatted into 3-way tensors representing individual images in each spectral band captured. For H2NMF, these tensors 
	are flattened so that the rows represent spectral bands (191 for HYDICE and 224 for AVIRIS) and the columns represent pixels.

	The HYDICE image is flattened from $1280\times 307\times 191$ to $191\times 392960$ and the AVIRIS image is likewise
	flattened from $8940\times 747\times 224$ to $224\times 6678180$. Unlike with document clustering, hyperspectral image sizes grow in pixels
	and not spectral bands. So, for both images, large scaling is impossible given our current data distribution.
	\LM{I think this is awkward and I'm not sure if we need to include it}

	\LM{DC: https://engineering.purdue.edu/~biehl/MultiSpec/hyperspectral.html}

	\LM{AVIRIS: https://aviris.jpl.nasa.gov/dataportal/}
